# 5. A Final Practice Problem 

Now for a fictional scenario. An emergency two-week randomized controlled trial of the experimental drug ZMapp is conducted to treat Ebola. (The control represents the usual standard of care for patients identified with Ebola, while the treatment is the usual standard of care plus the drug.) 

Here are the (fake) data. 

```{r read data}
d <- fread("../data/Ebola_rct2.csv")
head(d)
```

You are asked to analyze it. Patients' temperature and whether they are dehydrated is recorded on day 0 of the experiment, then ZMapp is administered to patients in the treatment group on day 1. Dehydration and temperature is again recorded on day 14.

1. Without using any covariates, answer this question with regression: What is the estimated effect of ZMapp (with standard error in parentheses) on whether someone was dehydrated on day 14? What is the p-value associated with this estimate?

```{r dehydration model}
mod_1 <- lm(dehydrated_day14~treat_zmapp,data=d)
summary(mod_1)
```
> This is significant and has a p value of 0.0066. The ATE of zmapp is -0.2377 (0.086).

2. Add covariates for dehydration on day 0 and patient temperature on day 0 to the regression from part (a) and report the ATE (with standard error). Also report the p-value.

```{r add pre-treatment measures}
mod_2 <- lm(dehydrated_day14~treat_zmapp+dehydrated_day0+temperature_day0,data=d)
summary(mod_2)
```
> The ate of receiving zmapp is -0.16554 with std error of 0.076 and a p value of 0.03113.

3. Do you prefer the estimate of the ATE reported in part (a) or part (b)? Why? Report the results of the F-test that you used to form this opinion. 

```{r test pre-treatment variable inclusion}
test_object <- var.test(mod_1,mod_2)
test_object
```

> I prefer part b since we have more covariates and it gives us more information and smaller standard error on our ATE.

4. The regression from part (2) suggests that temperature is highly predictive of dehydration. Add, temperature on day 14 as a covariate and report the ATE, the standard error, and the p-value.

```{r add pre-treatment temperature}
mod_3 <- lm(dehydrated_day14~treat_zmapp+dehydrated_day0+temperature_day0+temperature_day14,data=d)
summary(mod_3)
```

> Ate of -0.12 with a standard error of 0.078 and p value of 0.125.

5. Do you prefer the estimate of the ATE reported in part (b) or part (d)? What is this preference based on? 

> I prefer b since in part d treap_zmapp is no longer significant and we see that the temperatures are more significant when it comes to deheydration.

6. Now let's switch from the outcome of dehydration to the outcome of temperature, and use the same regression covariates as in the chunk titled `add pre-treatment measures`. Test the hypothesis that ZMapp is especially likely to reduce mens' temperatures, as compared to womens', and describe how you did so. What do the results suggest?

```{r heterogeneous treatment effects}
mod_4 <- lm(temperature_day14~treat_zmapp+dehydrated_day0+temperature_day0+dehydrated_day14+male,data=d)
summary(mod_4)
```

> Adding in male makes everything significant. We see a difference of 2 degrees in temperature difference in male and females so this confirms our hypothesis.

7. Which group -- those that are coded as `male == 0` or `male == 1` have better health outcomes in control? What about in treatment? How does this help to contextualize whatever heterogeneous treatment effect you might have estimated? 

```{r context for hte}
d[, .(Mean_Tem=mean(temperature_day14)), by=list(male,treat_zmapp)]

#d
d[,.(Mean_Deh=mean(dehydrated_day14)), by=list(male,treat_zmapp)]
#d
```

> Female has much better health outcomes in control. In treatment the males show a big improvement but end up around where the females are. There is definitely a difference between males and females which leads to a heterogeneous treatment effect. Next time blocking on gender would help the experiement.

8. Suppose that you had not run the regression in part (7). Instead, you speak with a colleague to learn about heterogeneous treatment effects. This colleague has access to a non-anonymized version of the same dataset and reports that they looked at heterogeneous effects of the ZMapp treatment by each of 80 different covariates to examine whether each predicted the effectiveness of ZMapp on each of 20 different indicators of health. Across these regressions your colleague ran, the treatment's interaction with gender on the outcome of temperature is the only heterogeneous treatment effect that he found to be statistically significant. They reason that this shows the importance of gender for understanding the effectiveness of the drug, because nothing else seemed to indicate why it worked. Bolstering your colleague's confidence, after looking at the data, they also returned to his medical textbooks and built a theory about why ZMapp interacts with processes only present in men to cure. Another doctor, unfamiliar with the data, hears your colleague's theory and finds it plausible. How likely do you think it is ZMapp works especially well for curing Ebola in men, and why? (This question is conceptual can be answered without performing any computation.)

> It is unlikely that zmapp works better for men than women. If we continue to look at men versus women and test it again and again we are bound to find some statistical significance. If we are testing repeatedly over many indicators it could very well be a false positive. 

9. Now, imagine that your colleague's fishing expedition did not happen, but that you had tested this heterogeneous treatment effect, and only this heterogeneous treatment effect, of your own accord. Would you be more or less inclined to believe that the heterogeneous treatment effect really exists? Why?

> I would be more inclinded to believe the heterogeneous treatment effect because I found it on my own and looks significant.

10. Now, imagine that your colleague's fishing expedition **did** happen, but that you on your own tested this and only this HTE, discover a positive result and conclude there is an effect. How does your colleague's behavior change the interpretation of your test? Does this seem fair or reasonable?

> I would be more inclinded to be skeptical of my results because of the fishing expedition. This seems fair that I will make sure my results are real and check with other replications of the experiement.
